---
title: "Hector Assignment"
author: "Natanel Ha"
date: "7/19/2021"
output: 
  html_document:
    toc: true
    toc_float: 
     collapsed: false
     smooth_scroll: false
    theme: paper 
---

#### Importing Libraries 
```{r importing, message=FALSE, warning=FALSE}
library(hector)
library(ggplot2)
library(dplyr)
library(tidyr)
```

### Running RCP 8.5

#### Creating Core
```{r core85, message=FALSE, warning=FALSE}
rcp85 <- system.file("input", "hector_rcp85.ini", package = "hector")
core85 <- newcore(rcp85, suppresslogging  = TRUE)
```

#### Run Core
```{r run85, message=FALSE, warning=FALSE, results='hide'}
run(core85)
```

#### Getting Results for Carbon Pools
```{r results85, message=FALSE, warning=FALSE}
result_vars <- c(ATMOSPHERIC_C(), SOIL_C(), VEG_C(), DETRITUS_C(), OCEAN_C())
results85 <- fetchvars(core85, 2000:2100, result_vars, scenario = "RCP 8.5")
```

#### Plotting Carbon Pools{.tabset}
##### Line Graph
```{r lineGraph85}
lineGraph85 <- ggplot(results85)+
  aes(x = year, y = value) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)")+
  theme_bw()+
  xlab("Year")
lineGraph85
```

##### Area Graph
```{r areaGraph85}
areaGraph85 <- ggplot(results85)+
  aes(x = year, y = value, group = scenario, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  geom_col(width = 1)+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab("Year")+
  theme_bw()
areaGraph85
```

##### Bar Graph
```{r barGraph85}
#Bar Graph Filtering
results85 %>%
  filter(year %% 100 == 0)->
  resultsCentury85

#Plotting
barPlot85 <- ggplot(resultsCentury85)+
  aes(x = as.character(year), y = value, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab("Year")+
  theme_bw()
barPlot85
```

##### Faceted Bar Graph
```{r splitBarPlot85}
#Bar Graph Filtering
results85 %>%
  filter(year %% 100 == 0)->
  resultsCentury85

#PLotting
splitBarPlot85 <- ggplot(resultsCentury85)+
  aes(x = as.character(year), y = value)+
  geom_bar(stat = "identity")+
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)") +
  xlab("Year")+
  theme_bw()
splitBarPlot85
```

#### Looking At Fluxes
```{r fluxes85, message=FALSE, warning=FALSE}
result_vars <- c(OCEAN_CFLUX(), LAND_CFLUX(), FFI_EMISSIONS())
results85flux <- fetchvars(core85, 2000:2100, result_vars, scenario = "RCP 8.5")
```

#### Calculating atmosphere flux
```{r atmosphereFlux85, message=FALSE, warning=FALSE}
results85flux %>%
  select(-units) %>%
  pivot_wider(names_from = variable) %>%
  mutate(atmosphere_flux = (ffi_emissions - atm_ocean_flux - atm_land_flux))%>%
  select(-ffi_emissions) %>%
  pivot_longer(3:5, names_to = "variable")->
  results85flux
```  

#### Plotting Fluxes {.tabset}
##### Line Graph 
```{r lineGraphFlux85}
fluxLine85 <- ggplot(results85flux)+
  aes(x = year, y = value, color = variable) +
  geom_line() +
  scale_color_discrete(labels = c("Land", "Ocean", "Atmosphere"))+
  guides(color = guide_legend(title = "Carbon Flux(Pg C/yr)"))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxLine85
```

##### Faceted Line Graph
```{r fluxFacetLine85}
fluxFacetLine85 <- ggplot(results85flux)+
  aes(x = year, y = value) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y",
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                             "atm_ocean_flux" = "Ocean Net Flux",
                                            "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxFacetLine85
```

##### Bar Graph 
```{r fluxBar85}
#Filtering data
results85flux %>%
  filter(year %% 100 == 0)->
  results85fluxCentury

#Plotting
fluxBar85 <- ggplot(results85fluxCentury)+
  aes(x = as.character(year), y = value)+
  geom_bar(stat = "identity")+
  facet_wrap(~variable, scales = "free_y",
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                              "atm_ocean_flux" = "Ocean Net Flux",
                                              "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)") +
  xlab("Year")+
  theme_bw()
fluxBar85
```

### Running RCP 4.5

#### Creating Core
```{r core45, message=FALSE, warning=FALSE}
rcp45 <- system.file("input", "hector_rcp45.ini", package = "hector")
core45 <- newcore(rcp45, suppresslogging  = TRUE)
```

#### Run Core
```{r run45, message=FALSE, warning=FALSE, results='hide'}
run(core45)
```

#### Getting Results for Carbon Pools
```{r results45, message=FALSE, warning=FALSE}
result_vars <- c(ATMOSPHERIC_C(), SOIL_C(), VEG_C(), DETRITUS_C(), OCEAN_C())
results45 <- fetchvars(core45, 2000:2100, result_vars, scenario = "RCP 4.5")
```

#### Plotting Carbon Pools{.tabset}
##### Line Graph
```{r lineGraph45}
lineGraph45 <- ggplot(results45)+
  aes(x = year, y = value) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)")+
  theme_bw()+
  xlab("Year")
lineGraph45
```

##### Area Graph
```{r areaGraph45}
areaGraph45 <- ggplot(results45)+
  aes(x = year, y = value, group = scenario, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  geom_col(width = 1)+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab("Year")+
  theme_bw()
areaGraph45
```

##### Bar Graph
```{r barGraph45}
#Bar Graph Filtering
results45 %>%
  filter(year %% 100 == 0)->
  resultsCentury45

#Plotting
barPlot45 <- ggplot(resultsCentury45)+
  aes(x = as.character(year), y = value, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab("Year")+
  theme_bw()
barPlot45
```

##### Faceted Bar Graph
```{r splitBarPlot45}
#Bar Graph Filtering
results45 %>%
  filter(year %% 100 == 0)->
  resultsCentury45

#PLotting
splitBarPlot45 <- ggplot(resultsCentury45)+
  aes(x = as.character(year), y = value)+
  geom_bar(stat = "identity")+
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)") +
  xlab("Year")+
  theme_bw()
splitBarPlot45
```

#### Looking At Fluxes
```{r fluxes45, message=FALSE, warning=FALSE}
result_vars <- c(OCEAN_CFLUX(), LAND_CFLUX(), FFI_EMISSIONS())
results45flux <- fetchvars(core45, 2000:2100, result_vars, scenario = "RCP 4.5")
```

#### Calculating atmosphere flux
```{r atmosphereFlux45, message=FALSE, warning=FALSE}
results45flux %>%
  select(-units) %>%
  pivot_wider(names_from = variable) %>%
  mutate(atmosphere_flux = (ffi_emissions - atm_ocean_flux - atm_land_flux))%>%
  select(-ffi_emissions) %>%
  pivot_longer(3:5, names_to = "variable")->
  results45flux
```  

#### Plotting Fluxes {.tabset}
##### Line Graph 
```{r lineGraphFlux45}
fluxLine45 <- ggplot(results45flux)+
  aes(x = year, y = value, color = variable) +
  geom_line() +
  scale_color_discrete(labels = c("Land", "Ocean", "Atmosphere"))+
  guides(color = guide_legend(title = "Carbon Flux(Pg C/yr)"))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxLine45
```

##### Faceted Line Graph
```{r fluxFacetLine45}
fluxFacetLine45 <- ggplot(results45flux)+
  aes(x = year, y = value) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y",
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                             "atm_ocean_flux" = "Ocean Net Flux",
                                            "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxFacetLine45
```

##### Bar Graph 
```{r fluxBar45}
#Filtering data
results45flux %>%
  filter(year %% 100 == 0)->
  results45fluxCentury

#Plotting
fluxBar45 <- ggplot(results45fluxCentury)+
  aes(x = as.character(year), y = value)+
  geom_bar(stat = "identity")+
  facet_wrap(~variable, scales = "free_y",
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                              "atm_ocean_flux" = "Ocean Net Flux",
                                              "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)") +
  xlab("Year")+
  theme_bw()
fluxBar45
```

### Comparing the two RCPs

#### Combining the two Datasets
```{r combining}
resultsC <- rbind(results85, results45)
resultsFlux <- rbind(results85flux, results45flux)
```

#### Plotting Carbon Pools{.tabset}
##### Line Graph
```{r lineGraphCompare}
lineGraphCompare <- ggplot(resultsC)+
  aes(x = year, y = value, color = scenario) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)")+
  guides(color = guide_legend(title = "Scenario"))+
  xlab("Year")+
  theme_bw()
lineGraphCompare
```

##### Area Graph
```{r areaGraphCompare}
areaGraphCompare <- ggplot(resultsC)+
  aes(x = year, y = value, group = scenario, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  facet_wrap(~scenario)+
  geom_col(width = 1)+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab("Year")+
  theme_bw()
areaGraphCompare
```

##### Bar Graph
```{r barGraphCompare}
#Bar Graph Filtering
resultsC %>%
  filter(year %% 100 == 0)->
  resultsCenturyCompare

#Plotting
barPlotCompare <- ggplot(resultsCenturyCompare)+
  aes(x = scenario, y = value, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  facet_wrap(~year)+
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab(NULL)+
  theme_bw()
barPlotCompare
```

##### Faceted Bar Graph
```{r splitBarPlotCompare}
#Bar Graph Filtering
resultsC %>%
  filter(year %% 100 == 0)->
  resultsCenturyCompare

#PLotting
splitBarPlotCompare <- ggplot(resultsCenturyCompare)+
  aes(x = as.character(year), y = value, fill = scenario)+
  geom_bar(stat = "identity", position = "dodge")+
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)") +
  xlab("Year")+
  theme_bw()
splitBarPlotCompare
```

#### Plotting Fluxes {.tabset}
##### Line Graph 
```{r lineGraphFluxCompare}
fluxLineCompare <- ggplot(resultsFlux)+
  aes(x = year, y = value, color = variable, linetype = scenario) +
  geom_line() +
  scale_color_discrete(labels = c("Land", "Ocean", "Atmosphere"))+
  guides(color = guide_legend(title = "Carbon Flux(Pg C/yr)"))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxLineCompare
```

##### Faceted Line Graph
```{r fluxFacetLineCompare}
fluxFacetLineCompare <- ggplot(resultsFlux)+
  aes(x = year, y = value, color = scenario) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y",
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                              "atm_ocean_flux" = "Ocean Net Flux",
                                              "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxFacetLineCompare
```

##### Bar Graph 
```{r fluxBarCompare}
#Filtering data
resultsFlux %>%
  filter(year %% 100 == 0)->
  resultsFluxCentury

#Plotting
fluxBarCompare <- ggplot(resultsFluxCentury)+
  aes(x = as.character(year), y = value, fill = scenario)+
  geom_bar(stat = "identity", position = "dodge")+
  facet_wrap(~variable, scales = "free_y",
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                              "atm_ocean_flux" = "Ocean Net Flux",
                                              "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)") +
  theme_bw()+
  xlab("Year")
fluxBarCompare
```

### Net Atmosphere flux below 0.5 Pg C/yr in 2100
Changing beta and q10_RH to get the Atmospheric flux to be below 0.5 Pg C/yr

#### Finding out what the current values of beta and Q10_RH
```{r currentValues}
beta <- fetchvars(core85, NA, BETA())
beta 
q10rh <- fetchvars(core85, NA, Q10_RH())
q10rh 

beta <- fetchvars(core45, NA, BETA())
beta 
q10rh <- fetchvars(core45, NA, Q10_RH())
q10rh 
```

#### Sensitivity Analysis Functions
##### Function to run Hector with a certain parameter change 
```{r param}
run_with_param <- function(core, parameter, value) {
  old_value <- fetchvars(core, NA, parameter)
  unit <- as.character(old_value[["units"]])
  setvar(core, NA, parameter, value, unit)
  reset(core)
  run(core)
  result_vars <- c(OCEAN_CFLUX(), LAND_CFLUX(), FFI_EMISSIONS())
  result <- fetchvars(core, 2000:2100, result_vars)
  result[["parameter_value"]] <- value
  result
}
```

#### Function to Run Hector with a range of parameter values
```{r paramRange}
run_with_param_range <- function(core, parameter, values) {
  mapped <- Map(function(x) run_with_param(core, parameter, x), values)
  Reduce(rbind, mapped)
}
```

#### Function to Perform Sensitivity Analysis 
```{r sensitivity}
sensitivity_analysis <- function(core, parameter, sequence){
  #Get Old value
  old_value <- fetchvars(core, NA, parameter)
  unit <- as.character(old_value[["units"]])
  
  #Sensitivity 
  sensitivity <- run_with_param_range(core, parameter, sequence)
  
  #Calculating Atmosphere Flux
  sensitivity %>%
    select(-units) %>%
    pivot_wider(names_from = variable) %>%
    mutate(atmosphere_flux = (ffi_emissions - atm_ocean_flux - atm_land_flux))%>%
    select(-ffi_emissions,-atm_ocean_flux,-atm_land_flux) ->
    sensitivity
  
  #Create plot
  sensitivity_plot <<- ggplot(sensitivity) +
    aes(x = year, y = atmosphere_flux, color = parameter_value, group = parameter_value) +
    geom_line() +
    ylab("Atmosphheric flux (Pg C/yr)")+
    guides(color = guide_colorbar(title = parameter)) +
    scale_color_viridis_c() 
  
  #Reset var
  setvar(core, NA, parameter, first(old_value$value), unit) 
  
  #Finding cutoff
  sensitivity %>%
    filter(year==2100, atmosphere_flux<=0.5)->
    working
  
  #Finding the parameter with least change 
  working %>%
    mutate(distance = abs(parameter_value - first(old_value$value)))%>%
    arrange(distance)->
    working
  
  return(first(working$parameter_value))
}
```

#### Function to Find Specific beta and q10_rh values that Work
```{r findValues}
find_values <- function(core, betaValues, q10rhValues){
  beta <- betaValues
  q10_rh <- c()
  for(val in betaValues){
    setvar(core, NA, BETA(), val, "(unitless)")
    q10_rh <- append(q10_rh, sensitivity_analysis(core, Q10_RH(), q10rhValues))
  }
  setvar(core, NA, BETA(), 0.36, "(unitless)")
  return(data.frame(beta, q10_rh))
}
```

#### Finding values for RCP 8.5 {.tabset}
##### Beta Plot
```{r betaPlot85}
sensitivity_analysis(core85, BETA(), seq(0,20,0.5))
sensitivity_plot
```

##### q10_rh Plot
```{r q10rhPlot85}
sensitivity_analysis(core85, Q10_RH(), seq(0.05,2,0.05))
sensitivity_plot
```

#### Working Values
```{r findingValues85, eval=FALSE, results='hide'}
find_values(core85, seq(14,19,0.5), seq(0.05,2,0.05))
```

```{r findingValues85table, echo=FALSE}
library(kableExtra)
find_values(core85, seq(14,19,0.5), seq(0.05,2,0.05)) %>%
  kbl %>%
  kable_styling(bootstrap_options = "striped", full_width = F, 
                position = "left")
```



#### Finding values for RCP 4.5 {.tabset}
##### Beta Plot
```{r betaPlot45}
sensitivity_analysis(core45, BETA(), seq(0,2,0.05))
sensitivity_plot
```

##### q10_rh Plot
```{r q10rhPlot45}
sensitivity_analysis(core45, Q10_RH(), seq(1,2,0.025))
sensitivity_plot
```

#### Working Values
```{r findingValues45, eval=FALSE, results='hide'}
find_values(core45, seq(0.36,0.54,0.02), seq(1.75,2,0.01))
```

```{r findingValues45table, echo=FALSE}
find_values(core45, seq(0.36,0.54,0.02), seq(1.75,2,0.01)) %>%
  kbl %>%
  kable_styling(bootstrap_options = "striped", full_width = F, 
                position = "left")
```
#### Shutting Down Cores
```{r shutdown, results='hide'}
shutdown(core85)
shutdown(core45)
```

#### Session Info: 
```{r sessionInfo, echo=FALSE}
sessionInfo()
```

