---
title: "Hector Assignment"
author: "Natanel Ha"
date: "7/19/2021"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: 
     collapsed: false
     smooth_scroll: true
    theme: paper 
---

This assignment refers to this github issue:
https://github.com/NatanelHa/Ha-Hector-Internship/issues/3 

The purpose is to get more familiar with working with the Hector simple climate model. 

##### Importing Libraries 
```{r importing, message=FALSE, warning=FALSE}
library(hector)
library(ggplot2)
library(dplyr)
library(tidyr)
```

## 1. RCP 8.5 Carbon Pools

Investigating how much carbon is in each pool in the Hector model in 2100 
compared to how much was in them in present day (I used from 2000 to 2100). 

First, I had to create and run a core based on RCP 8.5

#### Creating Core
```{r core85, message=FALSE, warning=FALSE}
rcp85 <- system.file("input", "hector_rcp85.ini", package = "hector")
core85 <- newcore(rcp85, suppresslogging  = TRUE)
```

#### Run Core
```{r run85, message=FALSE, warning=FALSE, results='hide'}
run(core85)
```

Then, I retrieved results from the carbon pools, and plotted them. 

#### Getting Results for Carbon Pools
```{r results85, message=FALSE, warning=FALSE}
result_vars <- c(ATMOSPHERIC_C(), SOIL_C(), VEG_C(), DETRITUS_C(), OCEAN_C())
results85 <- fetchvars(core85, 2000:2100, result_vars, scenario = "RCP 8.5")
```

#### Plotting Carbon Pools{.tabset}
##### Line Graph
```{r lineGraph85}
lineGraph85 <- ggplot(results85)+
  aes(x = year, y = value) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)")+
  theme_bw()+
  xlab("Year")
lineGraph85
```

##### Area Graph
```{r areaGraph85}
areaGraph85 <- ggplot(results85)+
  aes(x = year, y = value, group = scenario, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  geom_col(width = 1)+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab("Year")+
  theme_bw()
areaGraph85
```

##### Bar Graph
```{r barGraph85}
#Bar Graph Filtering
results85 %>%
  filter(year %% 100 == 0)->
  resultsCentury85

#Plotting
barPlot85 <- ggplot(resultsCentury85)+
  aes(x = as.character(year), y = value, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab("Year")+
  theme_bw()
barPlot85
```

##### Faceted Bar Graph
```{r splitBarPlot85}
#Bar Graph Filtering
results85 %>%
  filter(year %% 100 == 0)->
  resultsCentury85

#PLotting
splitBarPlot85 <- ggplot(resultsCentury85)+
  aes(x = as.character(year), y = value)+
  geom_bar(stat = "identity")+
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)") +
  xlab("Year")+
  theme_bw()
splitBarPlot85
```

#### Analysis 

From the line graph, it is evident that the ocean pool does not increase or decrease
in its amount of carbon from present day to 2100. Every other pool appears to have a 
similar positive increasing slope of increasing carbon from 2000 to 2100. 

From the area and bar graph, the relative sizes of the pools become more clear. 
The Ocean pool is the largest pool by far. The detritus pool is relatively a lot smaller so
its essentially not visible in the area and bar graph. 

From the bar graph and the faceted bar graph, it is evident that the the atmospheric
pool seems to have undergone the largest relative increase. 

## 2. RCP 8.5 Net Fluxes

Investigating how the rate of change of carbon (aka the fluxes) in each pool
in Hector is different between 2100 and present day (from 2000 to 2100)

#### Getting Results for Net Fluxes
```{r fluxes85, message=FALSE, warning=FALSE}
result_vars <- c(OCEAN_CFLUX(), LAND_CFLUX(), FFI_EMISSIONS())
results85flux <- fetchvars(core85, 2000:2100, result_vars, scenario = "RCP 8.5")
```

#### Calculating Atmosphere Flux
```{r atmosphereFlux85, message=FALSE, warning=FALSE}
results85flux %>%
  select(-units) %>%
  pivot_wider(names_from = variable) %>%
  mutate(atmosphere_flux = (ffi_emissions - atm_ocean_flux - atm_land_flux))%>%
  select(-ffi_emissions) %>%
  pivot_longer(3:5, names_to = "variable")->
results85flux
```  

#### Plotting Fluxes {.tabset}
##### Line Graph 
```{r lineGraphFlux85}
fluxLine85 <- ggplot(results85flux)+
  aes(x = year, y = value, color = variable) +
  geom_line() +
  scale_color_discrete(labels = c("Land", "Ocean", "Atmosphere"))+
  guides(color = guide_legend(title = "Carbon Flux(Pg C/yr)"))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxLine85
```

##### Faceted Line Graph
```{r fluxFacetLine85}
fluxFacetLine85 <- ggplot(results85flux)+
  aes(x = year, y = value) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y",
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                             "atm_ocean_flux" = "Ocean Net Flux",
                                            "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxFacetLine85
```

##### Bar Graph 
```{r fluxBar85}
#Filtering data
results85flux %>%
  filter(year %% 100 == 0)->
  results85fluxCentury

#Plotting
fluxBar85 <- ggplot(results85fluxCentury)+
  aes(x = as.character(year), y = value)+
  geom_bar(stat = "identity")+
  facet_wrap(~variable,
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                              "atm_ocean_flux" = "Ocean Net Flux",
                                              "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)") +
  xlab("Year")+
  theme_bw()
fluxBar85
```

#### Analysis

From the line graphs, we can see that all three fluxes have a largely positive slope. 
This means that the rate at which each pool increases in carbon is overall increasing. 
In the land pool, there is a slight dip at the end, meaning that the flux started 
to decrease towards the end of the century. 

From the bar graph, we can see the relative sizes of the fluxes. This shows
that the atmospheric flux is the largest, followed by the ocean flux, followed by land.

## 3. Comparing RCP 8.5 to RCP 4.5

First, I repeated the same analysis and created the same 
plots for RCP 4.5 that I did for RCP 8.5, in order to see 
how the results varied. 

### RCP 4.5 Carpon Pools

#### Creating Core
```{r core45, message=FALSE, warning=FALSE}
rcp45 <- system.file("input", "hector_rcp45.ini", package = "hector")
core45 <- newcore(rcp45, suppresslogging  = TRUE)
```

#### Run Core
```{r run45, message=FALSE, warning=FALSE, results='hide'}
run(core45)
```

#### Getting Results for Carbon Pools
```{r results45, message=FALSE, warning=FALSE}
result_vars <- c(ATMOSPHERIC_C(), SOIL_C(), VEG_C(), DETRITUS_C(), OCEAN_C())
results45 <- fetchvars(core45, 2000:2100, result_vars, scenario = "RCP 4.5")
```

#### Plotting Carbon Pools{.tabset}
##### Line Graph
```{r lineGraph45}
lineGraph45 <- ggplot(results45)+
  aes(x = year, y = value) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)")+
  theme_bw()+
  xlab("Year")
lineGraph45
```

##### Area Graph
```{r areaGraph45}
areaGraph45 <- ggplot(results45)+
  aes(x = year, y = value, group = scenario, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  geom_col(width = 1)+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab("Year")+
  theme_bw()
areaGraph45
```

##### Bar Graph
```{r barGraph45}
#Bar Graph Filtering
results45 %>%
  filter(year %% 100 == 0)->
  resultsCentury45

#Plotting
barPlot45 <- ggplot(resultsCentury45)+
  aes(x = as.character(year), y = value, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab("Year")+
  theme_bw()
barPlot45
```

##### Faceted Bar Graph
```{r splitBarPlot45}
#Bar Graph Filtering
results45 %>%
  filter(year %% 100 == 0)->
  resultsCentury45

#PLotting
splitBarPlot45 <- ggplot(resultsCentury45)+
  aes(x = as.character(year), y = value)+
  geom_bar(stat = "identity")+
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)") +
  xlab("Year")+
  theme_bw()
splitBarPlot45
```

#### Analysis 

Similar to RCP 8.5, we can see from the plots that each carbon pool increases, except
for the ocean pool which stays constant. We can also see that the ocean pool is the largest
and the detritus pool is the smallest. Similarly the atmospheric pool went through the largest
relative increase. 

However, the differ in that the line graphs show that the carbon levels start to level
out slighly by the end of the century. 

### RCP 4.5 Net Fluxes 

#### Getting Results for Net Fluxes
```{r fluxes45, message=FALSE, warning=FALSE}
result_vars <- c(OCEAN_CFLUX(), LAND_CFLUX(), FFI_EMISSIONS())
results45flux <- fetchvars(core45, 2000:2100, result_vars, scenario = "RCP 4.5")
```

#### Calculating atmosphere flux
```{r atmosphereFlux45, message=FALSE, warning=FALSE}
results45flux %>%
  select(-units) %>%
  pivot_wider(names_from = variable) %>%
  mutate(atmosphere_flux = (ffi_emissions - atm_ocean_flux - atm_land_flux))%>%
  select(-ffi_emissions) %>%
  pivot_longer(3:5, names_to = "variable")->
  results45flux
```  

#### Plotting Fluxes {.tabset}
##### Line Graph 
```{r lineGraphFlux45}
fluxLine45 <- ggplot(results45flux)+
  aes(x = year, y = value, color = variable) +
  geom_line() +
  scale_color_discrete(labels = c("Land", "Ocean", "Atmosphere"))+
  guides(color = guide_legend(title = "Carbon Flux(Pg C/yr)"))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxLine45
```

##### Faceted Line Graph
```{r fluxFacetLine45}
fluxFacetLine45 <- ggplot(results45flux)+
  aes(x = year, y = value) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y",
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                             "atm_ocean_flux" = "Ocean Net Flux",
                                            "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxFacetLine45
```

##### Bar Graph 
```{r fluxBar45}
#Filtering data
results45flux %>%
  filter(year %% 100 == 0)->
  results45fluxCentury

#Plotting
fluxBar45 <- ggplot(results45fluxCentury)+
  aes(x = as.character(year), y = value)+
  geom_bar(stat = "identity")+
  facet_wrap(~variable, 
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                              "atm_ocean_flux" = "Ocean Net Flux",
                                              "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)") +
  xlab("Year")+
  theme_bw()
fluxBar45
```

#### Analysis 

From the plots, we can see that the fluxes differ from the fluxes of RCP 8.5, in
that they all start of increasing, but around halfway through the century the fluxes
start to decrease. The atmospheric flux also sharply changes path and starts to increase
towards the end of the century.

From the bar chart, we can see that the ocean flux overall increased from start to end 
of the century, but the land and atmospheric pool are lower at the end of the century than
they started. 

### Comparing the two RCPs 

Second, I plotted the two RCPs on top of each other by combining
the datasets into one larger dataset. In each case I distinguished
between the two RCPs with color or line type. 

#### Combining the two Datasets
```{r combining}
resultsC <- rbind(results85, results45)
resultsFlux <- rbind(results85flux, results45flux)
```

#### Plotting Carbon Pools{.tabset}
##### Line Graph
```{r lineGraphCompare}
lineGraphCompare <- ggplot(resultsC)+
  aes(x = year, y = value, color = scenario) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)")+
  guides(color = guide_legend(title = "Scenario"))+
  xlab("Year")+
  theme_bw()
lineGraphCompare
```

##### Area Graph
```{r areaGraphCompare}
areaGraphCompare <- ggplot(resultsC)+
  aes(x = year, y = value, group = scenario, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  facet_wrap(~scenario)+
  geom_col(width = 1)+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab("Year")+
  theme_bw()
areaGraphCompare
```

##### Bar Graph
```{r barGraphCompare}
#Bar Graph Filtering
resultsC %>%
  filter(year %% 100 == 0)->
  resultsCenturyCompare

#Plotting
barPlotCompare <- ggplot(resultsCenturyCompare)+
  aes(x = scenario, y = value, fill = variable)+
  geom_bar(stat = "identity")+
  ylab("Carbon (Pg C)") +
  facet_wrap(~year)+
  scale_fill_discrete(labels = c("Atmosphere", "Detritus","Ocean", "Soil", "Vegetation"))+
  guides(fill = guide_legend(title = "Carbon Pools"))+
  xlab(NULL)+
  theme_bw()
barPlotCompare
```

##### Faceted Bar Graph
```{r splitBarPlotCompare}
#Bar Graph Filtering
resultsC %>%
  filter(year %% 100 == 0)->
  resultsCenturyCompare

#Plotting
splitBarPlotCompare <- ggplot(resultsCenturyCompare)+
  aes(x = as.character(year), y = value, fill = scenario)+
  geom_bar(stat = "identity", position = "dodge")+
  facet_wrap(~variable, scales = "free_y", 
             labeller = labeller(variable = c("atmos_c" = "Atmospheric",
                                              "veg_c" = "Vegetation",
                                              "soil_c" = "Soil",
                                              "detritus_c" = "Detritus",
                                              "ocean_c" = "Ocean")))+
  ylab("Carbon (Pg C)") +
  xlab("Year")+
  theme_bw()
splitBarPlotCompare
```

#### Analysis 

Comparing the two RCPs directly on top of each other, makes it more clear that the 
carbon pools went through a larger increase in RCP 8.5 than in RCP 4.5. It also more
clearly shows in the line graph how RCP 8.5 continues to increase while RCP 4.5 starts
to level off. Also, you can see that even though the two RCPs ocean pools stay constant, 
the ocean pool in RCP 8.5 has a larger pool of carbon than RCP 4.5

#### Plotting Fluxes {.tabset}
##### Line Graph 
```{r lineGraphFluxCompare}
fluxLineCompare <- ggplot(resultsFlux)+
  aes(x = year, y = value, color = variable, linetype = scenario) +
  geom_line() +
  scale_color_discrete(labels = c("Land", "Ocean", "Atmosphere"))+
  guides(color = guide_legend(title = "Carbon Flux(Pg C/yr)"))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxLineCompare
```

##### Faceted Line Graph
```{r fluxFacetLineCompare}
fluxFacetLineCompare <- ggplot(resultsFlux)+
  aes(x = year, y = value, color = scenario) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y",
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                              "atm_ocean_flux" = "Ocean Net Flux",
                                              "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)")+
  xlab("Year")+
  theme_bw()
fluxFacetLineCompare
```

##### Bar Graph 
```{r fluxBarCompare}
#Filtering data
resultsFlux %>%
  filter(year %% 100 == 0)->
  resultsFluxCentury

#Plotting
fluxBarCompare <- ggplot(resultsFluxCentury)+
  aes(x = as.character(year), y = value, fill = scenario)+
  geom_bar(stat = "identity", position = "dodge")+
  facet_wrap(~variable,
             labeller = labeller(variable = c("atm_land_flux" = "Land Net Flux",
                                              "atm_ocean_flux" = "Ocean Net Flux",
                                              "atmosphere_flux" = "Atmosphere Net Flux")))+
  ylab("Carbon Flux(Pg C/yr)") +
  theme_bw()+
  xlab("Year")
fluxBarCompare
```
#### Analysis 

By comparing the two RCPs on top of each other, we can see that for the large part
the fluxes in RCP 8.5 were always larger than RCP 4.5. The one exception is that 
towards the start of the century, the land flux was larger in RCP 4.5. 

We can also see how while in RCP 8.5, the fluxes increased while the fluxes 
in RCP 4.5 decreased in the second half of the century. 

## 4. Altering Parameters 
Changing beta and q10_RH to get the Atmospheric flux to be below 0.5 Pg C/yr

#### Finding out what the current values of beta and Q10_RH

To start out this task, I first found the default values for BETA()
and Q10_RH() in Hector. These values were the same for both RCPs.

```{r currentValues}
beta <- fetchvars(core85, NA, BETA())
beta 
q10rh <- fetchvars(core85, NA, Q10_RH())
q10rh 
```

### Sensitivity Analysis Functions

In order to find values of beta and q10_rh that would work, I modified and
added to the sensitivity analysis Vignette in the Hector Manual. This allowed
me to test and compile a range of different values of the two parameters. 

Credits to: https://jgcri.github.io/hector/articles/intro-to-hector.html#sensitivity-analysis 

A tour of the Hector R interface,
By Alexey Shiklomanov: 
2018-10-17

##### Function to run Hector with a certain parameter change 
This function runs a Hector core with a certain change in a specified parameter 
```{r param}
run_with_param <- function(core, parameter, value) {
  old_value <- fetchvars(core, NA, parameter)
  unit <- as.character(old_value[["units"]])
  setvar(core, NA, parameter, value, unit)
  reset(core)
  run(core)
  
  #Modified the results vars and years from Vignette
  #In order to look at the Atmospheric flux
  result_vars <- c(OCEAN_CFLUX(), LAND_CFLUX(), FFI_EMISSIONS())
  result <- fetchvars(core, 2000:2100, result_vars)
  result[["parameter_value"]] <- value
  result
}
```

#### Function to Run Hector with a range of parameter values
This function runs a range of values for a specified
parameter, using the previous function to run the model. 
```{r paramRange}
run_with_param_range <- function(core, parameter, values) {
  mapped <- Map(function(x) run_with_param(core, parameter, x), values)
  Reduce(rbind, mapped)
}
```

#### Function to Perform Sensitivity Analysis
This function performs the sensitivity analysis, creates a sensitivity plot, and returns
the cutoff for the closest the variable can be to the original value while still
having the Atmospheric flux below 0.5 Pg C/yr in 2100. 

This plot is a modified version from the Hector Vignette, and the rest was added
by myself. I put it in a function because it allowed me to run it repeatedly for different
RCPs and ranges of values. 
```{r sensitivity}
sensitivity_analysis <- function(core, parameter, sequence){
  #Get Old value
  old_value <- fetchvars(core, NA, parameter)
  unit <- as.character(old_value[["units"]])
  
  #Sensitivity 
  sensitivity <- run_with_param_range(core, parameter, sequence)
  
  #Calculating Atmosphere Flux
  sensitivity %>%
    select(-units) %>%
    pivot_wider(names_from = variable) %>%
    mutate(atmosphere_flux = (ffi_emissions - atm_ocean_flux - atm_land_flux))%>%
    select(-ffi_emissions,-atm_ocean_flux,-atm_land_flux) ->
    sensitivity
  
  #Create plot
  sensitivity_plot <<- ggplot(sensitivity) +
    aes(x = year, y = atmosphere_flux, color = parameter_value, group = parameter_value) +
    geom_line() +
    ylab("Atmosphheric flux (Pg C/yr)")+
    guides(color = guide_colorbar(title = parameter)) +
    scale_color_viridis_c() 
  
  #Reset var
  setvar(core, NA, parameter, first(old_value$value), unit) 
  
  #Finding cutoff
  sensitivity %>%
    filter(year==2100, atmosphere_flux<=0.5)->
    working
  
  #Finding the parameter with least change 
  working %>%
    mutate(distance = abs(parameter_value - first(old_value$value)))%>%
    arrange(distance)->
    working
  
  return(first(working$parameter_value))
}
```

#### Function to Find Specific beta and q10_rh values that Work
This function takes a range of betaValues, and for each of those betaValues
it finds the q10_rh needed to have the atmospheric flux below 0.5 Pg C/yr in 2100. 
It chooses the q10_rh closest to the original q10_rh value, by utilizing the above 
sensitivity analysis function. 
```{r findValues}
find_values <- function(core, betaValues, q10rhValues){
  beta <- betaValues
  q10_rh <- c()
  for(val in betaValues){
    setvar(core, NA, BETA(), val, "(unitless)")
    q10_rh <- append(q10_rh, sensitivity_analysis(core, Q10_RH(), q10rhValues))
  }
  setvar(core, NA, BETA(), 0.36, "(unitless)")
  return(data.frame(beta, q10_rh))
}
```

### Finding values for RCP 8.5

Using the above functions, I was able to find values of beta and q10_rh
that allow for an atmospheric flux below 0.5 Pg C/yr in 2100 in RCP 8.5

#### Sensitivity Plots {.tabset}
##### Beta Plot
```{r betaPlot85}
sensitivity_analysis(core85, BETA(), seq(0,20,0.5))
sensitivity_plot
```

The sensitivity analysis returns the value of Beta closest to the original 
that allows for below 0.5 Pg C/yr atmospheric flux in 2100, when q10_rh is left at 2. 
In this case it is 19. 

##### q10_rh Plot
```{r q10rhPlot85}
sensitivity_analysis(core85, Q10_RH(), seq(0.05,2,0.05))
sensitivity_plot
```

The sensitivity analysis returns the value of q10_rh closest to the original 
that allows for below 0.5 Pg C/yr atmospheric flux in 2100, when beta is left at 0.36. 
In this case it is NA, because no value of q10_rh would create a flux below 0.5 Pg C/yr when
beta is left at 0.36. 

#### Working Values
Finding pairs of values that work, meaning that they would create a value of 
0.5 Pg C/yr or less for the atmospheric flux in 2100. 
```{r findingValues85, eval=FALSE, results='hide'}
find_values(core85, seq(14,19,0.5), seq(0.05,2,0.05))
```
Table of Pairs of Working Values:
```{r findingValues85table, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
library(knitr)

as.data.frame(t(find_values(core85, seq(14,19,0.5), seq(0.05,2,0.05)))) %>% 
  kable(col.names = NULL) %>%  
  kable_styling(bootstrap_options = "striped", full_width = F, 
                position = "left")
```

#### Analysis

From the working values, we can see that beta would need to be over 14 in order for
the atmosphere to be below 0.5 Pg C/yr. This is a very drastic change from its original
value of 0.36. Therefore, I would infer it is not likely for the atmospheric flux to be
below 0.5 Pg C/yr in 2100 based on RCP 8.5. 

### Finding values for RCP 4.5

Using the above functions, I was able to find values of beta and q10_rh
that allow for an atmospheric flux below 0.5 Pg C/yr in 2100 in RCP 4.5

#### Sensitivity Plots {.tabset}
##### Beta Plot
```{r betaPlot45}
sensitivity_analysis(core45, BETA(), seq(0,2,0.05))
sensitivity_plot
```

The sensitivity analysis returns the value of Beta closest to the original 
that allows for below 0.5 Pg C/yr atmospheric flux in 2100, when q10_rh is left at 2. 
In this case it is 0.55. 

##### q10_rh Plot
```{r q10rhPlot45}
sensitivity_analysis(core45, Q10_RH(), seq(1,2,0.025))
sensitivity_plot
```

The sensitivity analysis returns the value of q10_rh closest to the original 
that allows for below 0.5 Pg C/yr atmospheric flux in 2100, when beta is left at 0.36. 
In this case it is 1.825. 

#### Working Values
Finding pairs of values that work, meaning that they would create a value of 
0.5 Pg C/yr or less for the atmospheric flux in 2100. 
```{r findingValues45, eval=FALSE, results='hide'}
find_values(core45, seq(0.36,0.54,0.02), seq(1.75,2,0.01))
```
Table of Pairs of Working Values:
```{r findingValues45table, echo=FALSE, message=FALSE, warning=FALSE}
as.data.frame(t(find_values(core45, seq(0.36,0.54,0.02), seq(1.75,2,0.01)))) %>% 
  kable(col.names = NULL) %>%  
  kable_styling(bootstrap_options = "striped", full_width = F, 
                position = "left")
```

#### Analysis 

All of the working values appear to be somewhat close to the original values, because
there are all within 0.5 of each other. I would say it would be plausible then
for atmospheric flux to be below 0.5 Pg C/yr in 2100 based on RCP 4.5.

#### Shutting Down Cores
```{r shutdown, results='hide'}
shutdown(core85)
shutdown(core45)
```

#### Session Info: 
```{r sessionInfo, echo=FALSE}
sessionInfo()
```

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
