---
title: "Soil-to-atmosphere C02 Flux Data Processing"
author: "Natanel Ha"
date: "7/1/2021"
output: html_document
---

### Importing Libraries
```{r importing, message=FALSE, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(kableExtra)
```

### Reading CSV Files 
```{r reading, message=FALSE, warning=FALSE}
collar_map <- readr::read_csv("collar_map.csv")
fluxes <- readr::read_csv("fluxes.csv")
```

### Creating a Long Data Table from fluxes and collar_map
```{r merge, message=FALSE, warning=FALSE}
fluxes %>%
  pivot_longer(-Collar, names_to="Date") %>% #Wide to Long
  filter(!is.na(value))%>%                   #Filter out NA
  left_join(collar_map, by="Collar")->        #Merging 
  fluxes_merged
```

### Computing Summary of Fluxes by Treatment
```{r summary}
fluxes_merged %>%
  group_by(Treatment) %>%
  summarise(mean = mean(value), N = n(), Std_dev = sd(value))%>% 
  kbl(digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, 
                position = "left")
```

### Boxplots with Overlaid Dots {.tabset}

####  Boxplots with Outliers
```{r boxplot}
fluxes_merged %>%
  ggplot(aes(x = Treatment, y = value))+
  geom_boxplot()+
  geom_jitter(alpha = 0.4, aes(color = Date))+
  ggtitle("Soil-to-atmosphere CO2 flux Boxplot by treatment")+
  ylab("Soil-to-atmosphere CO2 Flux (µmol/m2/s)")+
  theme_minimal()
```

####  Boxplots without Outliers
```{r boxplot.noOutliers, message=TRUE, warning=FALSE}
#Marking Which are Outliers
fluxes_merged %>% 
  group_by(Treatment) %>%
  summarise(median = median(value), IQR = IQR(value)) %>%
  right_join(fluxes_merged, by="Treatment") %>%
  mutate(not.outlier = as.numeric(abs(value-median)<1.5*IQR)) -> 
  filtered_fluxes

#Plotting Boxplot
filtered_fluxes %>%
  ggplot(aes(x = Treatment, y = value))+
  geom_boxplot(outlier.shape = NA)+
  geom_jitter(aes(color = Date, alpha = not.outlier))+
  scale_alpha_continuous(range = c(0, 1), guide = FALSE)+
  ylim(c(0,18))+
  ggtitle("Soil-to-atmosphere CO2 flux Boxplot by treatment")+
  ylab("Soil-to-atmosphere CO2 Flux (µmol/m2/s)")+
  theme_minimal()
```


### Line Graph with Error Bars
```{r linegraph, message=FALSE, warning=FALSE}
fluxes_merged %>%
  group_by(Treatment, Date) %>%
  summarise(mean = mean(value), Std_dev = sd(value)) %>%
  ggplot(aes(x = Date, y = mean, color = Treatment, group = Treatment))+
  geom_line()+ 
  geom_errorbar(aes(ymax = mean + Std_dev, 
                    ymin = mean - Std_dev), 
                    width = 0.2, 
                    alpha = 0.4)+
  ggtitle("Soil-to-atmosphere CO2 Flux Line Graph with Error bars")+
  ylab("Mean Soil-to-atmosphere CO2 Flux (µmol/m2/s)")+
  theme_minimal()
```


### Finding Out which Collars do not Appear in fluxes
Using anti_join, we can find out if any collars in the
metadata do not appear in the fluxes file. 
```{r antijoin}
collar_map %>%
  anti_join(fluxes, by="Collar")%>% 
  kbl %>%
  kable_styling(bootstrap_options = "striped", full_width = F, 
                position = "left")
```
It appears that Collar 34 does not appear in the fluxes file. 

Session Info: 
```{r sessionInfo, echo=FALSE}
sessionInfo()
```
