---
title: "Tracking Negative Emissions"
author: "Natanel Ha"
date: "8/4/2021"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: 
     collapsed: false
     smooth_scroll: true
    theme: paper
---

This document reflects done the work done by Natanel Ha on tracking negative
emissions scenarios (constructed with Jay Fuhrman's data) using the simple
climate model Hector's tracking feature. 

### Importing Libraries 
```{r importing, message=FALSE, warning=FALSE}
library(hector)
library(ggplot2)
library(dplyr)
library(tidyr)
```

### Establishing ini files
```{r inifiles, message=FALSE, warning=FALSE}
path <- "/Users/Natanel Ha/Documents/GitHub/Ha-Hector-Internship/New Scenarios/"
ini_file_26_SSP1 <- paste(path, "jay_SSP1.ini", sep = "")
ini_file_19_SSP1 <- paste(path, "jay_19_SSP1.ini", sep = "")
ini_file_26_SSP5 <- paste(path, "jay_SSP5.ini", sep = "")
ini_file_19_SSP5 <- paste(path, "jay_19_SSP5.ini", sep = "")
```


## Basic Tracking Plots
```{r basicTrackingFunction}
# tracking plot function
tracking_plot <- function(ini_file, start, stop, graph_type, pool, title) {
  # establish core
  core <- newcore(ini_file)

  # run core
  run(core)

  # Get Results
  results_with_diff <- get_tracking_data(core)
  results_with_diff

  # Filter out diff and year
  td <-
    results_with_diff %>%
    filter(pool_name != "Diff") %>%
    filter(year <= stop) %>%
    filter(year >= start) %>%
    mutate(source_amount = source_fraction * pool_value)

  # Changing Order
  td$pool_namef <- factor(td$pool_name, levels = c(
    "detritus_c_global",
    "veg_c_global",
    "soil_c_global",
    "earth_c",
    "atmos_c",
    "HL",
    "intermediate",
    "LL",
    "deep"
  ))


  # Set Theme
  theme_set(theme_minimal())

  if (pool != "all") {
    td %>%
      filter(pool_name == pool) ->
    td
  }

  # Graph of Fractional Portion
  if (graph_type == "fraction") {
    areaGraph <- ggplot(td) +
      aes(x = year, y = source_fraction, fill = source_name) +
      geom_area() +
      facet_wrap(~pool_namef,
        labeller = labeller(pool_namef = c(
          "detritus_c_global" = "Detritus",
          "veg_c_global" = "Vegetation",
          "soil_c_global" = "Soil",
          "earth_c" = "Earth",
          "atmos_c" = "Atmosphere",
          "HL" = "High Level Ocean",
          "intermediate" = "Intermediate Ocean",
          "LL" = "Low Level Ocean",
          "deep" = "Deep Ocean"
        ))
      ) +
      scale_fill_manual(
        limits = c(
          "detritus_c_global",
          "veg_c_global",
          "soil_c_global",
          "earth_c",
          "atmos_c",
          "HL",
          "intermediate",
          "LL",
          "deep"
        ),
        labels = c(
          "Detritus",
         "Vegetation",
        "Soil",
          "Earth",
          "Atmosphere",
          "High Level Ocean",
          "Intermediate Ocean",
          "Low Level Ocean",
          "Deep Ocean"
        ),
        values = c(
          "#DDCC77",
          "#999933",
          "#44AA99",
          "#117733",
          "#DDDDDD",
          "#882255",
          "#AA4499",
          "#88CCEE",
          "#332288"
        )
      ) +
      guides(fill = guide_legend(title = "Carbon Pools")) +
      ylab("Source Fraction") +
      ggtitle(title) +
      xlab("Year")

    # Graph of the Amount of Carbon
  } else {
    areaGraph <- ggplot(td) +
      aes(x = year, y = source_amount, fill = source_name) +
      geom_bar(stat = "identity") +
      facet_wrap(~pool_namef,
        scales = "free_y",
        labeller = labeller(pool_namef = c(
          "detritus_c_global" = "Detritus",
          "veg_c_global" = "Vegetation",
          "soil_c_global" = "Soil",
          "earth_c" = "Earth",
          "atmos_c" = "Atmosphere",
          "HL" = "High Level Ocean",
          "intermediate" = "Intermediate Ocean",
          "LL" = "Low Level Ocean",
          "deep" = "Deep Ocean"
        ))
      ) +
      scale_fill_manual(
        limits = c(
          "detritus_c_global",
          "veg_c_global",
          "soil_c_global",
          "earth_c",
          "atmos_c",
          "HL",
          "intermediate",
          "LL",
          "deep"
        ),
        labels = c(
          "Detritus",
          "Vegetation",
          "Soil",
          "Earth",
          "Atmosphere",
          "High Level Ocean",
          "Intermediate Ocean",
          "Low Level Ocean",
          "Deep Ocean"
        ),
        values = c(
          "#DDCC77",
          "#999933",
          "#44AA99",
          "#117733",
          "#DDDDDD",
          "#882255",
          "#AA4499",
          "#88CCEE",
          "#332288"
        )
      ) +
      geom_col(width = 1) +
      guides(fill = guide_legend(title = "Carbon Pools")) +
      ylab("Source Amount (Pg C)") +
      ggtitle(title) +
      xlab("Year")
  }

  # Shutdown Core
  shutdown(core)

  areaGraph
}
```

### Basic Fraction Plots {.tabset}

#### RCP 2.6 SSP1
```{r frac26s1, echo=FALSE}
tracking_plot(
  ini_file_26_SSP1, 2005, 2100,
  "fraction", "all", "RCP 2.6 SSP1"
)
```


#### RCP 2.6 SSP5
```{r frac26s5, echo=FALSE}
tracking_plot(
  ini_file_26_SSP5, 2005, 2100,
  "fraction", "all", "RCP 2.6 SSP5"
)
```

#### RCP 1.9 SSP1
```{r frac19s1, echo=FALSE}
tracking_plot(
  ini_file_19_SSP1, 2005, 2100,
  "fraction", "all", "RCP 1.9 SSP1"
)
```

#### RCP 1.9 SSP5
```{r frac19s5, echo=FALSE}
tracking_plot(
  ini_file_19_SSP5, 2005, 2100,
  "fraction", "all", "RCP 1.9 SSP5"
)
```

### Basic Plots of Amounts of Carbon {.tabset}

#### RCP 2.6 SSP1
```{r am26s1, echo=FALSE}
tracking_plot(
  ini_file_26_SSP1, 2005, 2100,
  "amount", "all", "RCP 2.6 SSP1"
)
```


#### RCP 2.6 SSP5
```{r am26s5, echo=FALSE}
tracking_plot(
  ini_file_26_SSP5, 2005, 2100,
  "amount", "all", "RCP 2.6 SSP5"
)
```

#### RCP 1.9 SSP1
```{r am19s1, echo=FALSE}
tracking_plot(
  ini_file_19_SSP1, 2005, 2100,
  "amount", "all", "RCP 1.9 SSP1"
)
```

#### RCP 1.9 SSP5
```{r am19s5, echo=FALSE}
tracking_plot(
  ini_file_19_SSP5, 2005, 2100,
  "amount", "all", "RCP 1.9 SSP5"
)
```


## Earth Pool Examination 
```{r earthFunc}
earth_plot <- function(ini_file, start, stop, type, scenario) {
  # Establish core
  core <- newcore(ini_file, suppresslogging = TRUE)

  # Run core
  run(core)

  # Get Results
  results <- get_tracking_data(core)

  # Calculating source anount
  results %>%
    filter(pool_name == "earth_c") %>%
    filter(year >= start) %>%
    filter(year <= stop) %>%
    mutate(source_amount = source_fraction * pool_value) ->
  results

  # Finding earth_c values in start
  # The year negative emissions starts
  earth_start <-
    results %>%
    filter(source_name == "earth_c")

  earth_start_carbon <-
    first(earth_start$source_amount)

  earth_start_fraction <-
    first(earth_start$source_fraction)

  # Calculating difference from start
  results %>%
    mutate(source_amount = source_amount - earth_start_carbon * (source_name == "earth_c")) %>%
    mutate(source_fraction = source_fraction - earth_start_fraction * (source_name == "earth_c")) ->
  results

  if (type == "amount") {
    # Plotting in area graph of amount
    areaGraph <- ggplot(results) +
      aes(x = year, y = source_amount, fill = source_name) +
      geom_area() +
      scale_fill_manual(
        limits = c(
          "detritus_c_global",
          "veg_c_global",
          "soil_c_global",
          "earth_c",
          "atmos_c",
          "HL",
          "intermediate",
          "LL",
          "deep"
        ),
        labels = c(
          "Detritus",
          "Vegetation",
          "Soil",
          "Earth",
          "Atmosphere",
          "High Level Ocean",
          "Intermediate Ocean",
          "Low Level Ocean",
          "Deep Ocean"
        ),
        values = c(
          "#DDCC77",
          "#999933",
          "#44AA99",
          "#117733",
          "#DDDDDD",
          "#882255",
          "#AA4499",
          "#88CCEE",
          "#332288"
        )
      ) +
      guides(fill = guide_legend(title = "Carbon Pools")) +
      ylab("Source Amount (Pg C)") +
      ggtitle(paste("Earth Pool: Net Change from", start), 
              subtitle = scenario) +
      xlab("Year")
    return(areaGraph)
  } else {
    # Plotting in area graph of fraction
    areaGraph2 <- ggplot(results) +
      aes(x = year, y = source_fraction, fill = source_name) +
      geom_area() +
      scale_fill_manual(
        limits = c(
          "detritus_c_global",
          "veg_c_global",
          "soil_c_global",
          "earth_c",
          "atmos_c",
          "HL",
          "intermediate",
          "LL",
          "deep"
        ),
        labels = c(
          "Detritus",
          "Vegetation",
          "Soil",
          "Earth",
          "Atmosphere",
          "High Level Ocean",
          "Intermediate Ocean",
          "Low Level Ocean",
          "Deep Ocean"
        ),
        values = c(
          "#DDCC77",
          "#999933",
          "#44AA99",
          "#117733",
          "#DDDDDD",
          "#882255",
          "#AA4499",
          "#88CCEE",
          "#332288"
        )
      ) +
      guides(fill = guide_legend(title = "Carbon Pools")) +
      ylab("Source Fraction") +
      ggtitle(paste("Earth Pool: Net Change from", start), 
              subtitle = scenario) +
      xlab("Year")
    return(areaGraph2)
  }
}
```

### Earth Fraction Plots {.tabset}

#### RCP 2.6 SSP1
```{r earth_frac26s1, echo=FALSE}
earth_plot(
  ini_file_26_SSP1, 2005, 2100,
  "fraction", "RCP 2.6 SSP1"
)
```


#### RCP 2.6 SSP5
```{r earth_frac26s5, echo=FALSE}
earth_plot(
  ini_file_26_SSP5, 2005, 2100,
  "fraction", "RCP 2.6 SSP5"
)
```

#### RCP 1.9 SSP1
```{r earth_frac19s1, echo=FALSE}
earth_plot(
  ini_file_19_SSP1, 2005, 2100,
  "fraction", "RCP 1.9 SSP1"
)
```

#### RCP 1.9 SSP5
```{r earth_frac19s5, echo=FALSE}
earth_plot(
  ini_file_19_SSP5, 2005, 2100,
  "fraction", "RCP 1.9 SSP5"
)
```

### Earth Plots of Amounts of Carbon {.tabset}

#### RCP 2.6 SSP1
```{r earth_am26s1, echo=FALSE}
earth_plot(
  ini_file_26_SSP1, 2005, 2100,
  "amount", "RCP 2.6 SSP1"
)
```


#### RCP 2.6 SSP5
```{r earth_am26s5, echo=FALSE}
earth_plot(
  ini_file_26_SSP5, 2005, 2100,
  "amount", "RCP 2.6 SSP5"
)
```

#### RCP 1.9 SSP1
```{r earth_am19s1, echo=FALSE}
earth_plot(
  ini_file_19_SSP1, 2005, 2100,
  "amount", "RCP 1.9 SSP1"
)
```

#### RCP 1.9 SSP5
```{r earth_am19s5, echo=FALSE}
earth_plot(
  ini_file_19_SSP5, 2005, 2100,
  "amount", "RCP 1.9 SSP5"
)
```

## Function for increase in each pool
```{r diffFunc}
# Tracking plot Function
difference_plot <- function(ini_file, start, stop, pool, title) {
  core <- newcore(ini_file, suppresslogging = TRUE)

  # run core
  run(core)

  # Get td
  td <- get_tracking_data(core)

  # Calculating Source amount and Diff
  td %>%
    filter(pool_name != "Diff") %>%
    mutate(source_amount = source_fraction * pool_value) %>%
    group_by(pool_name, source_name) %>%
    mutate(differ = source_amount - lag(source_amount)) ->
  td

  # Creating better labels
  td$pool_namef <- factor(td$pool_name, levels = c(
    "detritus_c_global",
    "veg_c_global",
    "soil_c_global",
    "earth_c",
    "atmos_c",
    "HL",
    "intermediate",
    "LL",
    "deep"
  ))

  # Filtering out years and NA
  td %>%
    filter(year >= start) %>%
    filter(year <= stop) %>%
    filter(!is.na(differ)) ->
  td

  # A plot of all pools
  if (pool != "all") {
    td %>%
      filter(pool_name == pool) ->
    td
  }
  areaGraph <- ggplot(td) +
    aes(x = year, y = differ, fill = source_name) +
    geom_area() +
    facet_wrap(~pool_namef,
      scales = "free_y",
      labeller = labeller(pool_namef = c(
        "detritus_c_global" = "Detritus",
        "veg_c_global" = "Vegetation",
        "soil_c_global" = "Soil",
        "earth_c" = "Earth",
        "atmos_c" = "Atmosphere",
        "HL" = "High Level Ocean",
        "intermediate" = "Intermediate Ocean",
        "LL" = "Low Level Ocean",
        "deep" = "Deep Ocean"
      ))
    ) +
    scale_fill_manual(
      limits = c(
        "detritus_c_global",
        "veg_c_global",
        "soil_c_global",
        "earth_c",
        "atmos_c",
        "HL",
        "intermediate",
        "LL",
        "deep"
      ),
      labels = c(
        "Detritus",
        "Vegetation",
        "Soil",
        "Earth",
        "Atmosphere",
        "High Level Ocean",
        "Intermediate Ocean",
        "Low Level Ocean",
        "Deep Ocean"
      ),
      values = c(
        "#DDCC77",
        "#999933",
        "#44AA99",
        "#117733",
        "#DDDDDD",
        "#882255",
        "#AA4499",
        "#88CCEE",
        "#332288"
      )
    ) +
    guides(fill = guide_legend(title = "Carbon Pools")) +
    ylab("Change from Previous Year (Pg C)") +
    ggtitle(title) +
    xlab("Year")

  areaGraph
}
```

### Difference Plots {.tabset}
#### RCP 2.6 SSP1
```{r dif26s1, echo=FALSE}
difference_plot(ini_file_26_SSP1, 2005, 2100, "all", "RCP 2.6 SSP1")
```

#### RCP 2.6 SSP5
```{r dif26s5, echo=FALSE}
difference_plot(ini_file_26_SSP5, 2005, 2100, "all", "RCP 2.6 SSP5")
```

#### RCP 1.9 SSP1
```{r dif19s1, echo=FALSE}
difference_plot(ini_file_19_SSP1, 2005, 2100, "all", "RCP 1.9 SSP1")
```

#### RCP 1.9 SSP5
```{r dif19s5, echo=FALSE}
difference_plot(ini_file_19_SSP5, 2005, 2100, "all", "RCP 1.9 SSP5")
```

### Difference Earth Pool {.tabset}
#### RCP 2.6 SSP1
```{r earthDif26s1, echo=FALSE}
difference_plot(ini_file_26_SSP1, 2005, 2100, "earth_c", "RCP 2.6 SSP1")
```

#### RCP 2.6 SSP5
```{r earthDif26s5, echo=FALSE}
difference_plot(ini_file_26_SSP5, 2005, 2100, "earth_c", "RCP 2.6 SSP5")
```

#### RCP 1.9 SSP1
```{r earthDif19s1, echo=FALSE}
difference_plot(ini_file_19_SSP1, 2005, 2100, "earth_c", "RCP 1.9 SSP1")
```

#### RCP 1.9 SSP5
```{r earthDif19s5, echo=FALSE}
difference_plot(ini_file_19_SSP5, 2005, 2100, "earth_c", "RCP 1.9 SSP5")
```

### Session Info: 
```{r sessionInfo, echo=FALSE}
sessionInfo()
```

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>

